Secure Composition \\ of Robust and Optimising Compilers \vspace{-1.5em}

### 2024-05-29 csf2/main.tex
nits

This paper uses a general notion of robust preservation~\cite{abate2021extacc} that considers compilers that use languages with different trace models. 
To this end, considering a source trace $\src{\trace}$ and a target trace $\trg{\trace}$, there is a relation ($\sim$) describing the effect of a corresponding compiler (see \Cref{sec:casestud:rtp}). 
This relation induces the following two projection functions~\cite{abate2021extacc}: (1) the \emph{existential image} $\tau_\sim\left(\src{\pi}\right)$ and (2) the \emph{universal image} $\sigma_\sim\left(\trg{\pi}\right)$.
These projections map source-level (resp. target-level) properties to target-level (resp. source-level) properties in a way that identifies the ``same'' property across languages. 
The case study of this paper uses the universal image, since some considered properties, such as \gls*{ss}, are not definable in a higher-level language that, e.g., does not model speculation.
% For self-containment, the universal image is defined as follows~\cite{abate2021extacc}:
% 
\begin{definition}[Universal Image]
% [Existential and Universal Image]
\label{def:universal:img}\label{def:sigma}
  % \[
  %   \tau_\sim\left(\src{\pi}\right) := 
  %     \left\{ 
  %       \trg{\trace} \mid \exists \src{\trace}\ldotp \src{\trace}\sim\trg{\trace}, \text{ and } \src{\trace}\in\src{\pi} 
  %     \right\}
  % \]
  \[ 
    \sigma_\sim\left(\trg{\pi}\right) := 
      \left\{ 
        \src{\trace} \mid \forall \trg{\trace}\ldotp \text{if }\src{\trace}\sim\trg{\trace}, \text{ then } \trg{\trace}\in\trg{\pi} 
      \right\}
  \]
\end{definition}
\noindent
With this projection function, we define a more general version of robust preservation as follows~\cite{abate2021extacc}.
% For a \bul{compiler $\cc{\src{L}}{\trg{L}}$ to robustly preserve a class of source properties $\src{\class}$}, if for any \rul{property $\src{\pi}$ of that class $\src{\class}$ and programs $\src{p}$ written in $\src{L}$} where \iul{$\src{\progvar}$ robustly satisfies $\src{\pi}$}, then \oul{the compilation of $\src{\progvar}$, $\cc{\src{L}}{\trg{L}}\left(\src{p}\right)$, must robustly satisfy $\tau_\sim\left(\src{\pi}\right)$}.
% 
% \begin{definition}[Robust Preservation with $\tau_\sim$]\label{def:rtp:tau}
%   % $\;$\\
%   % \vspace{-1em}
%   % \begin{nscenter}
%   % Compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves $\class$, 
%   \bul{$\rtptau{\cc{\src{L}}{\trg{L}}}{\src{\class}}{\sim}$}
%   %, iff 
%   $\isdef$
%   \rul{$\forall \src{\pi}\in\src{\class}, \src{p}\in\src{L},$} if \iul{$\rsat{\src{\progvar}}{\src{\pi}}$}, then \oul{$\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\tau_\sim{\left(\src{\pi}\right)}}$}.
%   % \end{nscenter}
% \end{definition}
% 
A \bul{compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves a class of target properties $\trg{\class}$}, if for any \rul{property $\trg{\pi}$ of class $\trg{\class}$ and programs $\src{p}$}, where \iul{$\src{\progvar}$ robustly satisfies $\sigma_\sim\left(\trg{\pi}\right)$}, \oul{the compilation of $\src{\progvar}$, $\cc{\src{L}}{\trg{L}}\left(\src{p}\right)$, robustly satisfies $\trg{\pi}$}.

@@

The language also adds user annotations $\obj{\securitytag{}}$ for the secrecy of variables, which can be either private (high secrecy) $\obj{\lock}$ or public (low secrecy) $\obj{\unlock}$.
Security tags $\obj{\securitytag{}}$ are arranged in the usual secrecy lattice~\cite{zdancewicphd}, where $\obj{\lock}\sqsubseteq\obj{\securitytag{}}$ and $\obj{\securitytag{}}\sqsubseteq\obj{\unlock}$.

@@

Finally, let us consider a trace $\irl{\trace}\in\mssafe$ and understand what is that is related to via $\sim^{\Ltrg}_{\Lms}$.
% 
{\em All} traces $\trg{\trace}$ with $\trg{\trace}\sim^{\Ltrg}_{\Lms}\irl{\trace}$ are identical to $\irl{\trace}$ except for get and set actions, which require for in-bound accesses: this clearly respect $\mssafe$.
%

>>>>

This paper uses a general notion of robust preservation~\cite{abate2021extacc} that considers compilers that use languages with different trace models. 
To this end, considering a source trace $\src{\trace}$ and a target trace $\trg{\trace}$, there is a relation ($\sim$) describing the effect of a corresponding compiler (see \Cref{sec:casestud:rtp}). 
This relation induces the following two projection functions~\cite{abate2021extacc}: (1) the \emph{existential image} $\tau_\sim\left(\src{\pi}\right)$ and (2) the \emph{universal image} $\sigma_\sim\left(\trg{\pi}\right)$.
These projections map source-level (resp. target-level) properties to target-level (resp. source-level) properties in a way that identifies the ``same'' property across languages. 
The case study of this paper uses the universal image, since some considered properties, such as \gls*{ss}, are not definable in a higher-level language that, e.g., does not model speculation.
% For self-containment, the universal image is defined as follows~\cite{abate2021extacc}:
% 
\begin{definition}[Universal Image]
% [Existential and Universal Image]
\label{def:universal:img}\label{def:sigma}
  % \[
  %   \tau_\sim\left(\src{\pi}\right) := 
  %     \left\{ 
  %       \trg{\trace} \mid \exists \src{\trace}\ldotp \src{\trace}\sim\trg{\trace}, \text{ and } \src{\trace}\in\src{\pi} 
  %     \right\}
  % \]
  \[ 
    \sigma_\sim\left(\trg{\pi}\right) := 
      \left\{ 
        \src{\trace} \mid \forall \trg{\trace}\ldotp \text{if }\src{\trace}\sim\trg{\trace}, \text{ then } \trg{\trace}\in\trg{\pi} 
      \right\}
  \]
\end{definition}
\noindent
With this projection function, we define a more general version of robust preservation as follows~\cite{abate2021extacc}.
% For a \bul{compiler $\cc{\src{L}}{\trg{L}}$ to robustly preserve a class of source properties $\src{\class}$}, if for any \rul{property $\src{\pi}$ of that class $\src{\class}$ and programs $\src{p}$ written in $\src{L}$} where \iul{$\src{\progvar}$ robustly satisfies $\src{\pi}$}, then \oul{the compilation of $\src{\progvar}$, $\cc{\src{L}}{\trg{L}}\left(\src{p}\right)$, must robustly satisfy $\tau_\sim\left(\src{\pi}\right)$}.
% 
% \begin{definition}[Robust Preservation with $\tau_\sim$]\label{def:rtp:tau}
%   % $\;$\\
%   % \vspace{-1em}
%   % \begin{nscenter}
%   % Compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves $\class$, 
%   \bul{$\rtptau{\cc{\src{L}}{\trg{L}}}{\src{\class}}{\sim}$}
%   %, iff 
%   $\isdef$
%   \rul{$\forall \src{\pi}\in\src{\class}, \src{p}\in\src{L},$} if \iul{$\rsat{\src{\progvar}}{\src{\pi}}$}, then \oul{$\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\tau_\sim{\left(\src{\pi}\right)}}$}.
%   % \end{nscenter}
% \end{definition}
% 
A \bul{compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves a class of target properties $\trg{\class}$}, if for any \rul{property $\trg{\pi}$ of class $\trg{\class}$ and programs $\src{p}$}, where \iul{$\src{\progvar}$ robustly satisfies $\sigma_\sim\left(\trg{\pi}\right)$}, \oul{the compilation of $\src{\progvar}$, we have that $\cc{\src{L}}{\trg{L}}\left(\src{p}\right)$ robustly satisfies $\trg{\pi}$}.

@@

The language also adds user annotations $\obj{\securitytag{}}$ for the secrecy of variables, which can be either private (high secrecy) $\obj{\lock}$ or public (low secrecy) $\obj{\unlock}$.
Security tags $\obj{\securitytag{}}$ are arranged in the usual secrecy lattice~\cite{zdancewicphd}, where $\obj{\unlock}\sqsubseteq\obj{\lock}$.
% $\obj{\lock}\sqsubseteq\obj{\securitytag{}}$ and $\obj{\securitytag{}}\sqsubseteq\obj{\unlock}$.

@@

Finally, let us consider a trace $\irl{\trace}\in\mssafe$ and understand what is that is related to via $\sim^{\Ltrg}_{\Lms}$.
% 
{\em All} traces $\trg{\trace}$ with $\trg{\trace}\sim^{\Ltrg}_{\Lms}\irl{\trace}$ are identical to $\irl{\trace}$ except for get and set actions, which require for in-bound accesses (as stated in \Cref{subsec:cs:ms}): this clearly respect $\mssafe$.
%
